\documentclass[9pts]{article}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage[compact]{titlesec}

\input{glyphtounicode}
\pdfgentounicode=1

\titlespacing{\section}{0pt}{*0}{*0}
\titlespacing{\subsection}{0pt}{*0}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}

\topmargin=0.0in %length of margin at the top of the page (1 inch added by default)
\oddsidemargin=-0.2in %length of margin on sides for odd pages
\evensidemargin=-0.2in %length of margin on sides for even pages
\textwidth=7.0in %How wide you want your text to be
\marginparwidth=0.0in
\headheight=0pt %1in margins at top and bottom (1 inch is added to this value by default)
\headsep=0pt %Increase to increase white space in between headers and the top of the page
\textheight=9.0in %How tall the text body is allowed to be on each page
\pagenumbering{gobble}
\setlength{\parindent}{0in}

\date{\vspace{-5ex}}
\title{\vspace{-5ex} \vspace{-5ex}}


% Begin editing here

\author{\Huge Mohammad Yousuf Minhaj Zia}

\begin{document}

\maketitle

\centerline{
\href{mailto:yousuf.zia@u.nus.edu}{yousuf.zia@u.nus.edu} \textbar \hspace{1pt}
\href{mailto:yzia2000@gmail.com}{yzia2000@gmail.com} \textbar \hspace{1pt} 
\href{https://yzia2000.github.io/blog}{Blog} \textbar \hspace{1pt} 
\href{https://github.com/yzia2000}{\faGithub \hspace{1pt} yzia2000} \textbar \hspace{1pt}
\href{https://www.linkedin.com/in/mohammad-yousuf-minhaj-zia-ab555396}{\faLinkedin} \textbar \hspace{1pt}
+91 70217 91005 \textbar \hspace{1pt} 
+65 9835 4761 
}

\line(1,0){470}\\

\section*{EDUCATION}
\subsection*{National University of Singapore (NUS) \hfill Aug 18 - Present}
\begin{itemize}
    \item Bachelor of Engineering (Computer Engineering), Hons with minor in Data Engineering (restricted minor)
    \item Current CAP: 4.53 (Expected First Class Honours) Dean's List 2019/2020 FoE and SoC
    \item Expected Date of Graduation: May 2022
\end{itemize}

\section*{WORK EXPERIENCE}
\subsection*{Software Engineer Part-Time, Glints \hfill May 21 - Present}
\begin{itemize}
    \item Implemented backend business logic for internal product in GraphQL and REST API.
    \item Architected a Kafka pipeline and stream processor in Scala with FP principles, which aggregates on Postgres change data events and sinks to Elasticsearch bringing down sync frequency from 24h to $<1$s.
    \item Implemented an Elasticsearch indexing solution for offline and online integration.
    \item Deployed Scala and Kafka Streams application with CI/CD and Kubernetes helm charts.
    \item Backend and Data Module Code Approver of a product team where I review PRs before being merged to staging and communicate directly with stakeholders to verify requirements.
    \item Investigated and resolved production OOMs and latency issues in NodeJS, Redis, Postgres services through query optimizations.
    \item As a scrum member specified stories, backlog tasks and participated in sprints in an automated Jira workflow
\end{itemize}

\subsection*{Co-founder, NUS Fellowmark \href{https://github.com/Fellowmark/fellowmark}{\faGithub} \href{https://youtu.be/LVmKodrE8e0}{\faYoutube} \hfill Aug 20 - Present}
\begin{itemize}
    \item Co-founded a web application for schools and universities for distributed documentation peer review.
    \item Implemented backend business logic in Golang and Postgres which includes authentication, basic CRUD and a fileserver to serve file uploads and downloads.
    \item Implemented frontend in ReactJS with Material UI.
\end{itemize}

\subsection*{Co-founder, ZiMS \href{https://github.com/zims-live}{\faGithub} \hfill May 20 - Present}
\begin{itemize}
    \item Founded a suite of open-source video conferencing applications currently for general purpose and education verticles.
    \item Architected frontend and backend applications with CI/CD, security practices, latency, bandwidth and idempotency.
    \item Currently deployed by Vitaminds in Netherlands to connect mental health professionals with people in need of help.
\end{itemize}

\subsection*{Intern Software Engineer in Test, Autodesk AutoCAD \hfill Jul 20 - Dec 20}
\begin{itemize}
    \item Migrated 400 test cases from TestComplete to in-house API automation for AutoCAD verticals, ACA and AME, making test execution over 90\% faster and leaner reducing test server costs.
    \item Implemented a VBScript parser in Python to tag GUI operations in approx. 7000 TestComplete test cases and designed analysis metrics to identify suitable candidates for migration.
    \item Architected and implemented a GUI handler tool using Win32 API, UIAutomation, ObjectARX and .NET which is automation framework and product independent.
\end{itemize}

\subsection*{ Intern Machine Learning, NExT++ Research Center \href{https://github.com/GelliFrancesco/assetpriceprediction}{\faGithub} \hfill May 19 - Dec 19}
\begin{itemize}
    \item Designed and tested financial sentiment models on financial news for stock market prediction research back-tested models with algorithmic trading libraries zipline and pyfolio (10\% return without transaction costs).
    \item Trained and tested financial lexicon models, Google BERT and deep learning models using Pytorch.
    \item Processed and filtered approx. 13 million financial news articles to optimize model performance.
\end{itemize}

\section*{SKILLS}
{\large \bf Proficient}
Scala, GraphQL, Postgres, Kafka, Typescript, Javscript, Go, C, C\#, C++, Java,
Swagger/OpenAPI, Python, HTML, CSS, React, Docker, NoSQL, CI/CD, Testing
Automation, Agile, JIRA, Pytorch, Pandas, Numpy.

{\large \bf Exposure}
Kubernetes, GCP Compute Engine, AWS EC2, Selenium, Rust, Lua, .NET

\end{document}
